---
title: "`r params$title`"
author: "`r params$author`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  word_document:
    reference_docx: word_template.docx
  pdf_document:
    toc: true
    number_sections: true
params:
  title: "Meta-Analysis Report"
  author: "Author"
  protocol: NULL
  results: NULL
  he_results: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
library(ggplot2)
```

# Executive Summary

This report presents the results of a systematic review and meta-analysis.

# Protocol

**Population:** `r if(!is.null(params$protocol)) params$protocol$population else "Not specified"`

**Intervention:** `r if(!is.null(params$protocol)) params$protocol$intervention else "Not specified"`

**Comparator:** `r if(!is.null(params$protocol)) params$protocol$comparator else "Not specified"`

**Outcomes:** `r if(!is.null(params$protocol)) paste(params$protocol$outcomes, collapse = ", ") else "Not specified"`

# Methods

## Search Strategy

A comprehensive search was conducted in accordance with PRISMA guidelines.

## Data Extraction

Data were extracted independently by two reviewers.

## Statistical Analysis

Meta-analysis was performed using a random-effects model with the REML estimator.

# Results

## Study Characteristics

```{r study-table}
# Placeholder for study characteristics table
```

## Meta-Analysis Results

```{r results-summary}
if (!is.null(params$results)) {
  for (outcome in names(params$results)) {
    result <- params$results[[outcome]]
    cat(sprintf("\n### %s\n\n", outcome))
    cat(sprintf("Pooled effect: %.3f (95%% CI: %.3f to %.3f)\n\n",
                result$pooled_effect, result$ci_lower, result$ci_upper))
    cat(sprintf("Heterogeneity: I² = %.1f%%, τ² = %.3f\n\n",
                result$i_squared, result$tau_squared))
  }
}
```

## Heterogeneity Assessment

Heterogeneity was assessed using the I² statistic and Q test.

## Publication Bias

Funnel plots and Egger's test were used to assess publication bias.

# Health Economic Analysis

```{r he-results}
if (!is.null(params$he_results)) {
  cat(sprintf("ICER: £%.2f per QALY\n\n", params$he_results$icer))
  cat(sprintf("Incremental QALYs: %.3f\n\n", params$he_results$inc_qalys))
  cat(sprintf("Incremental Costs: £%.2f\n\n", params$he_results$inc_costs))
}
```

# Discussion

## Summary of Findings

The meta-analysis demonstrates...

## Limitations

Limitations include...

## Conclusions

In conclusion...

# References

References would be listed here.

# Appendices

## Appendix A: Search Strategy

Full search strategy...

## Appendix B: Excluded Studies

List of excluded studies with reasons...

## Appendix C: Risk of Bias Assessment

Risk of bias tables...
